\LARGE \bf Steering a Swarm Using Global Inputs and Swarm Statistics

### 2016-08-15 journalSwarmControl/Introduction.tex
mary's edits on minimum
mean \pm std for numbers
added new swarm control code

Our goal was to test several scenarios involving large-scale human-swarm interaction (HSI), and to do so with a statistically-significant sample size. Towards this end, we created \href{http://www.swarmcontrol.net/show_results}{SwarmControl.net}, an open-source, online testing platform suitable for inexpensive deployment and data collection on a scale not yet seen in swarm robotics research. Screenshots from this platform are shown in Fig.~\ref{fig:5experiments}.  \href{https://github.com/crertel/swarmmanipulate.git}{All code} \href{http://www.swarmcontrol.net/show_results}{and experimental results} are posted online, \cite{Chris-Ertel2013}. \todo{TODO: Chris, is 2016 code ready to upload? link to 2016 code}

>>>>

Our goal was to test several scenarios involving large-scale human-swarm interaction (HSI), and to do so with a statistically-significant sample size. Towards this end, we created \href{http://www.swarmcontrol.net/show_results}{SwarmControl.net}, an open-source, online testing platform suitable for inexpensive deployment and data collection on a scale not yet seen in swarm robotics research. Screenshots from this platform are shown in Fig.~\ref{fig:5experiments}.  \href{https://github.com/crertel/swarmmanipulate.git}{All code} \href{http://www.swarmcontrol.net/show_results}{and experimental results} are posted online at \cite{Chris-Ertel2016}.

### 2016-08-15 journalSwarmControl/experiment.tex
mary's edits on minimum
mean \pm std for numbers
added new swarm control code

$\mathbf{M}_{BFS}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 robots, pushing the object to goal using BFS required $\mu=183$, $\sigma=179$ s while Policy Iteration required $\mu=90$, $\sigma=35$ s.
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

@@

In 10 simulations with 100 robots, pushing the object to goal without a repulsive potential field failed in two of twelve runs. No failures occurred with the repulsive potential field.  Of successful trials, completion time without repulsive potential fields required $\mu=245, \sigma=135$ s while using repulsive potential fields required $\mu=90, \sigma=35$ s.
%In 10 simulations with 100 robots, completion time without repulsive potential fields required $\mu=245, \sigma=135$s while using repulsive potential fields required $\mu=90, \sigma=35$.

@@

In 10 simulations with 100 robots, completion time without outlier rejection required $\mu=245, \sigma=135$ s while using outlier rejection required $\mu=90, \sigma=35$ s.
%\todo{report results of 10 simulations with and without regions.  Give mean and std}

@@

In rare cases during simulations the swarm may become trapped in a local minima of \eqref{eq:potentialfield}.
If the swarm mean position does not change for five seconds, the swarm is assumed to be in a local minima and is commanded to move toward the previous corner. As soon as the mean position changes, normal control resumes.

>>>>

$\mathbf{M}_{BFS}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 robots, pushing the object to goal using BFS required 183$\pm$179 s while Policy Iteration required 90$\pm$35 s (mean$\pm$std).
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

@@

In 10 simulations with 100 robots, pushing the object to goal without a repulsive potential field failed in two of twelve runs. No failures occurred with the repulsive potential field.  Of successful trials, completion time without repulsive potential fields required 245$\pm$135 s while using repulsive potential fields required 90$\pm$35 s (mean$\pm$std).
%In 10 simulations with 100 robots, completion time without repulsive potential fields required $\mu=245, \sigma=135$s while using repulsive potential fields required $\mu=90, \sigma=35$.

@@

In 10 simulations with 100 robots, completion time without outlier rejection required 245$\pm$135 s while using outlier rejection required 90$\pm$35 s (mean$\pm$std).
%\todo{report results of 10 simulations with and without regions.  Give mean and std}

@@

In rare cases during simulations the swarm may become trapped in a local minimum of \eqref{eq:potentialfield}.
If the swarm mean position does not change for five seconds, the swarm is assumed to be in a local minimum and is commanded to move toward the previous corner. As soon as the mean position changes, normal control resumes.

### 2016-08-15 journalSwarmControl/realExperiment.tex
mary's edits on minimum
mean \pm std for numbers
added new swarm control code

Above the table, an overhead machine vision system tracks the swarm. The vision system identifies obstacles by color segmentation, determines the corners  (used to decrease  variance), the object by color segmentation, and identifies robots using color segmentation and circle detection with a circular Hough transform. Code for the vision, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central by \cite{Shahrokhi2015MDP}.

@@

%\begin{figure*}
%\begin{center}
%	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
%	\begin{overpic}[width=0.6\columnwidth]{SetUp.pdf}%\put(1,75){A}
%	\end{overpic}\\
%	\begin{overpic}[width=0.35\columnwidth]{AllShapesR.pdf}%\put(-0,85){B}
%	\end{overpic}
%	\begin{overpic}[width=0.35\columnwidth]{PotentialExp.pdf}%\put(-0,85){C}
%	\end{overpic}
%\end{center}
%\caption{\label{fig:setup}
%(Top) Hardware platform. (Lower left) Four shapes used for hardware experiments. (Lower right) Visualization of potential field. }
%\end{figure*}

@@

%\begin{figure}
%\begin{center}
%	\includegraphics[width=\columnwidth]{XYMeanControl.eps}
%\end{center}
%\caption{\label{fig:meanRobotFig}
%Mean Control experiment with kilobots.
%}
%\end{figure}

@@

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace. The same controller as in the simulation, Alg.~\ref{alg:BlockPushing}, but with discretized control inputs, was coded in {\sc Matlab}, available at \todo{matlab link}.  
Trials were run until the object COM entered the goal region.  The trials ran for \{24:25, 57:37, 50:00, 36:02, 45:07\} minutes.  This is a mean of 42:38 and a standard deviation of 12:51 minutes. 
A circular object completed in 52:35 minutes. 
A square object completed in 114:31 minutes. 
A triangular object completed in XX:YY minutes.

>>>>

Above the table, an overhead machine vision system tracks the swarm. The vision system identifies obstacles by color segmentation, determines the corners  (used to decrease  variance), the object by color segmentation, and identifies robots using color segmentation and circle detection with a circular Hough transform.

@@

@@

@@

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central by \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std). 
A circular object completed in 3155 s. 
A square object completed in 6871 s. 
\todo{A triangular object completed in ??:?? minutes.}
